Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-11 paper.qmd
Added squares for the positions

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "Light Grays") +
  geom_rect(aes(xmin = 0.8, xmax = 0.9, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#e41a1c", linewidth = 0.7) +
  geom_rect(aes(xmin = 0.75, xmax = 0.85, ymin = 0.8, ymax = 0.95),
               fill = "transparent", color = "#377eb8", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.25, xmax = 0.35, ymin = 0.55, ymax = 0.7),
               fill = "transparent", color = "#4daf4a", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.5, xmax = 0.6, ymin = 0.15, ymax = 0.3),
               fill = "transparent", color = "#984ea3", linewidth = 0.7) 
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```

@@

img_right_top <- c(6048, 6650, 5119)

@@

img_middle <- c(3443, 7404, 7242)

@@

img_right_bottom <- c(7098, 6456, 2)

>>>>

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "Light Grays") +
  geom_rect(aes(xmin = 0.8, xmax = 0.9, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#e41a1c", linewidth = 0.7) +
  geom_rect(aes(xmin = 0.75, xmax = 0.85, ymin = 0.8, ymax = 0.95),
               fill = "transparent", color = "#377eb8", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.45, xmax = 0.55, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#4daf4a", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#984ea3", linewidth = 0.7) 
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```

@@

img_right_top <- c(4795, 259, 6564)

@@

img_middle <- c(1069, 4604, 3579)

@@

#img_right_bottom <- c(1695, 5338, 2805)
img_right_bottom <- c(2035, 7710, 2517)
